Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-02-24 awipev-CO2.Rmd

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
       dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
     dyLegend(show = "follow")   %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

>>>>

durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
       dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
     dyLegend(show = "follow")   %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@
